---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dislib

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

"dislib" or disease library is a package to provide information about the diseases and its mortality rate. The original data are from [Our world in Data](https://ourworldindata.org/what-does-the-world-die-from).

## Installation

You can install the development version of dislib from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-KrisanatA")
```

## Example

```{r example}
library(dislib)
```

The mortality rate overtime for Cardiovascular diseases in Australia:

```{r}
plot_dis("Cardiovascular diseases", "Australia")
```

What diseases has the highest mortality rate in Australia for 2019:

```{r}
dis_summary("Australia", 2019)
```

