---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dislib

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

"dislib" or disease library is a package to provide information about the diseases and their mortality rate. The original data are from [Our world in Data](https://ourworldindata.org/what-does-the-world-die-from).

You can access the package website through this [link](https://etc5523-2022.github.io/rpkg-KrisanatA/)

## Installation

You can install the development version of dislib from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-KrisanatA")
```

## Examples

```{r example}
library(dislib)
```

### The mortality rate overtime for Cardiovascular diseases in Australia:

```{r}
plot_dis(disease = "Cardiovascular diseases", country = "Australia")
```

To examine how the mortality rate has evolved over time for the country and years chosen.

### What diseases have the highest mortality rate in Australia for 2019:

```{r}
dis_summary(country = "Australia", year = 2019)
```

This function allows users to see the top 10 highest mortality rates for the country and year chosen.

### Launching shiny app:

```{r, eval = FALSE}
run_app()
```

