---
title: "dislib package"
format: 
  revealjs:
    theme: beige
editor: visual
---

```{r, include = FALSE}
library(dislib)
library(kableExtra)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 4,
  fig.align = "center",
  out.width = "100%",
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
```


## dislib package

Package to provide information about the diseases and their mortality rate.

<br>

**About the package:** <br>This package contains mortality data from [Our World in Data](https://ourworldindata.org/what-does-the-world-die-from) 

This data include countries, codes, continents, years, diseases, mortality rates info.

<br>

**Author:** Krisanat Anukarnsakulchularp 29803829


## dislib package

<br>

**Install package:** These are the step needed to download the package.

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false
install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-KrisanatA")
```


## dislib package

**Purpose:** 

To provide easier access to the mortality rate data and allow users to analyse the information based on their interest.

<br>**Package Summary:**

-   Dataset

-   3 main functions

-   Information list


## Function 1: plot_dis()

:::: {.columns}

::: {.column width="50%"}
**About:**

The function plot graph in relation to the disease and country input.

This visual aid allows users to examine the change in a more effective way.


:::

::: {.column width="50%"}

**Function:**

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false
plot_dis(disease = "Cardiovascular Diseases", country = "Australia")
```

```{r}
#| echo: false
plot_dis(disease = "Cardiovascular diseases", country = "Australia")
```

:::

::::


## Function 2: dis_summary() {.scrollable}

:::: {.columns}

::: {.column width="50%"}
**About:**

The function showcase the mortality rate ranking for each country and year.

:::

::: {.column width="50%"}

In contrast to *plot_dis()* function, *dis_summary()* focuses on individual element.

:::

::::

**Function:**

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false
dis_summary(country = "Australia", year = 2019)
```

```{r}
#| echo: false
dis_summary(country = "Australia", year = 2019)
```


## Function 3: run_app()

**About:**

The function is created to launch app.

This act like shorcut to the interactive app for the users

<br>

**Function:**

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false
run_app()
```


## Information list function

With the dislib package, there are limitation to the input.

<br>

The function to help with that are:

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false
year_list(country = "Australia")
```

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false
country_list()
```

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false
disease_list()
```

<br>

As the package contain certain years, countries, and diseases.


## dislib package

:::: {.columns}

::: {.column width="50%"}

**Data:** *mortality* data

<br>

**Function:**

-   plot_dis()

-   dis_summary()

-   run_app()

:::

::: {.column width="50%"}

<br>

<br>

<br>

-   year_list()

-   country_list()

-   disease_list()

:::

::::






